From Reversible Programs to \\ Univalent Universes and Back

### 2017-07-05 upi.tex
citation
minor tweaks

\noindent It is worthwhile mentioning that the above derivation could also be
drawn as one (large!) commutative diagram in an appropriate category, with each
$\byisotwo{-}$ as a $2$-arrow (and representing a natural isomorphism).
See~\cite{Shulmann} for that interpretation.

@@

Of course, we can obtain another (trivial) example from $\mathbb{1}$:
$P : \mathbb{1} \rightarrow \mathbb{U}$, defined as
$P(\star) = \mathbb{1}$. $P$ is univalent as both $\star \equiv \star$ and
$\mathbb{1} \simeq \mathbb{1}$ each have a single inhabitant.

@@

{\small
\[\def\arraystretch{1.2}\begin{array}{rcll}
\AgdaFunction{$\dbracket{ \_ }_1$}  &:& (\bt \leftrightarrow \bt) \rightarrow `\bt \equiv `\bt \\
\AgdaFunction{$\dbracket{ \id }_1$} &=& `\mathbf{id}\\
\AgdaFunction{$\dbracket{ \swap }_1$} &=& `\mathbf{not}\\
\AgdaFunction{$\dbracket{ ! p }_1$} &=& (\dbracket{ p }_1)^{-1} \\
\AgdaFunction{$\dbracket{ p \odot q }_1$} &=& \dbracket{ p }_1 \circ \dbracket{ p }_1\\
\end{array}
\]}

>>>>

\noindent It is worthwhile mentioning that the above derivation could also be
drawn as one (large!) commutative diagram in an appropriate category, with each
$\byisotwo{-}$ as a $2$-arrow (and representing a natural isomorphism).  See
Shulman's draft book~\cite{shulman} for that interpretation.

@@

Of course, we can obtain another (trivial) example from the unit type:
$P : \mathbb{1} \rightarrow \mathbb{U}$, defined as
$P(\star) = \mathbb{1}$. $P$ is univalent as both $\star \equiv \star$ and
$\mathbb{1} \simeq \mathbb{1}$ each have a single inhabitant.

@@

\[\def\arraystretch{1.2}\begin{array}{rcll}
\AgdaFunction{$\dbracket{ \_ }_1$}  &:& (\bt \leftrightarrow \bt) \rightarrow `\bt \equiv `\bt \\
\AgdaFunction{$\dbracket{ \id }_1$} &=& `\mathbf{id}\\
\AgdaFunction{$\dbracket{ \swap }_1$} &=& `\mathbf{not}\\
\AgdaFunction{$\dbracket{ ! p }_1$} &=& (\dbracket{ p }_1)^{-1} \\
\AgdaFunction{$\dbracket{ p \odot q }_1$} &=& \dbracket{ p }_1 \circ \dbracket{ p }_1\\
\end{array}
\]
